Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-08 dryad/README.Rmd
adding newick files of source chronograms

@@

	File 2 Name: Sanchez-Reyes_etal_2022_table_2.csv    
	File 2 Description: CSV (comma separated values) file containing a summary of node age (in Million years) data from table S1.

@@

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.csv    
	File XXX Description: CSV (comma separated values) file

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf    
	File XXX Description: PDF file of

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.csv    
	File XXX Description: CSV (comma separated values) file

>>>>

```{r, echo=FALSE}
file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv")
```

@@

	File 2 Name: Sanchez-Reyes_etal_2022_table_2.csv    
	File 2 Description: CSV (comma separated values) file containing a summary of node age (in Million years) data from table 1.

@@

```{r, echo=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")

```

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.csv    
	File XXX Description: CSV (comma separated values) file containing results from the Fringillidae example. Names and ages (in Million years) of nodes from source chronograms that have been congruified to nodes of the chosen tree topology shown in Figure 4B of the manuscript.

```{r, echo=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")

```

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf    
	File XXX Description: PDF version of file Sanchez-Reyes_etal_2022_supplementary_table_S1.csv

```{r, echo=FALSE}
file.copy(from = ".../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.csv")

```

  File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.csv    
	File XXX Description: CSV (comma separated values) file containing a summary of node age data (in Million years) from table S1.

```{r, echo=FALSE}
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf")

```
